Create Figures and Tables

### 2023-07-24 Codes/1_3_bootstrap_avgyield.rmd
updates

  #--- raw data for prediction ---#
  data_for_pred <-
    CJ(
      balance = seq(min(data_boot$balance), max(data_boot$balance), length = 50),
      sat_cat = unique(data_boot$sat_cat)
    ) %>%
    # .[, sat := parse_number(gsub("\\,.*", "", sat_cat))] %>%
    .[, sat := case_when(
      sat_cat == "[39.4,82]" ~ 40,
      sat_cat == "(82,194]" ~ 194,
      sat_cat == "(194,708]" ~ 348,
      sat_cat == "dryland" ~ 0
    )] %>%
    .[is.na(sat), sat := 0] %>%
    # === can be any sc_code (need to shift yield for "average" county) ===#
    .[, sc_code := sc_base] %>%
    .[, sc_dry := sc_dry_base] %>%
    # === can be any year (need to shift yield for "average" year) ===#
    .[, year := 2009] %>%
    # === fake yield data (necessary to take advantage of predict.gam) ===#
    .[, yield := 0] %>%
    .[, type := "pred"] %>%
    .[, dry_or_not := fifelse(sat_cat == "dryland", 1, 0) %>% factor()]

@@

  ir_share_res <-
    gam(
      acres_ratio ~
        s(sat, k = 3, m = 2) +
        s(balance_avg, k = 3, m = 2) +
        factor(state_name) +
        factor(year),
      data = ir_share_data,
      # weight = ~acres,
      family = binomial
    )

  share_pred_data_corn <-
    CJ(
      sat = seq(
        min(ir_share_data$sat),
        max(ir_share_data$sat),
        length = 100
      ),
      balance_avg = mean(ir_share_data$balance_avg),
      year = 2016,
      state_name = "Nebraska"
    )

  ir_share_hat_data <-
    predict(
      ir_share_res,
      newdata = share_pred_data_corn,
      type = "response",
      se.fit = TRUE
    )

@@

```{r}
boot_results_data <-
  data.table(
    crop = c("Corn", "Soybean"),
    data = list(data_corn, data_soy)
  ) %>%
  mutate(boot_results = purrr::map(data, \(data) {
    parallel::mclapply(
      1:1000,
      function(i) bootstrap(i, data, sc_base, sc_dry_base),
      mc.cores = 12
    ) %>%
      rbindlist()
  })) %>%
  dplyr::mutate(se_data = purrr::map(boot_results, \(boot_results){
    boot_results[, .(avg_yield_sd = sd(avg_yield), dif_yield_sd = sd(dif_yield)), by = .(sat_cat, balance, type)]
  }))

>>>>

  #--- raw data for prediction ---#
  data_for_pred <-
    CJ(
      balance = seq(min(data_boot$balance), max(data_boot$balance), length = 50),
      sat = c(0, 40, 194, 348, 602)
    ) %>%
    # .[, sat := parse_number(gsub("\\,.*", "", sat_cat))] %>%
    .[, sat_cat := case_when(
      sat == 40 ~ "[39.4,82]",
      sat == 194 ~ "(82,194]",
      sat == 348 ~ "(194,708]",
      sat == 602 ~ "(194,708]",
      sat == 0 ~ "dryland"
    )] %>%
    # === can be any sc_code (need to shift yield for "average" county) ===#
    .[, sc_code := sc_base] %>%
    .[, sc_dry := sc_dry_base] %>%
    # === can be any year (need to shift yield for "average" year) ===#
    .[, year := 2009] %>%
    # === fake yield data (necessary to take advantage of predict.gam) ===#
    .[, yield := 0] %>%
    .[, type := "pred"] %>%
    .[, dry_or_not := fifelse(sat_cat == "dryland", 1, 0) %>% factor()]

@@

  ir_share_res <-
    gam(
      acres_ratio ~
        s(sat, k = 3, m = 2) +
        s(balance_avg, k = 3, m = 2) +
        factor(state_year),
      data = ir_share_data,
      # weight = ~acres,
      family = binomial
    )

  share_pred_data <-
    CJ(
      sat = seq(
        min(ir_share_data$sat),
        max(ir_share_data$sat),
        length = 100
      ),
      balance_avg = mean(ir_share_data$balance_avg),
      year = 2016,
      state_year = "Nebraska_2009"
    )

  ir_share_hat_data <-
    predict(
      ir_share_res,
      newdata = share_pred_data,
      type = "response",
      se.fit = TRUE
    )

@@

```{r}
boot_results_data <-
  data.table(
    crop = c("Corn", "Soybean"),
    data = list(data_corn, data_soy)
  ) %>%
  mutate(boot_results = purrr::map(data, \(data) {
    parallel::mclapply(
      1:1000,
      function(i) bootstrap(i, data, sc_base, sc_dry_base),
      mc.cores = parallel::detectCores() - 2
    ) %>%
      rbindlist()
  })) %>%
  dplyr::mutate(se_data = purrr::map(boot_results, \(boot_results){
    boot_results[, .(avg_yield_sd = sd(avg_yield), dif_yield_sd = sd(dif_yield)), by = .(sat_cat, balance, type)]
  }))

### 2023-07-24 Codes/2_figures_tables.rmd
updates

```{r}
results <- readRDS("Shared/Results/reg_results_data.rds")
```

@@

g_corn <-
  ggplot() +
  geom_sf(data = counties_corn_all, fill = "gray") +
  geom_sf(data = counties_corn_ir, aes(fill = sat * 0.3048)) +
  scale_fill_viridis_c(
    name = "Aquifer Thickness (meter)",
    guide = guide_colorbar(
      title.position = "top"
    )
  ) +
  geom_sf(data = states_of_interest, fill = NA, color = "blue") +
  geom_sf(data = hpa_simplified, fill = NA, color = "red") +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(1, "cm")
  ) +
  ggtitle("A. Corn")

g_soy <-
  ggplot() +
  geom_sf(data = counties_soy_all, fill = "gray") +
  geom_sf(data = counties_soy_ir, aes(fill = sat * 0.3048)) +
  scale_fill_viridis_c(
    name = "Aquifer Thickness (meter)",
    guide = guide_colorbar(
      title.position = "top"
    )
  ) +
  geom_sf(data = states_of_interest, fill = NA, color = "blue") +
  geom_sf(data = hpa_simplified, fill = NA, color = "red") +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(1, "cm")
  ) +
  ggtitle("B. Soybean")

@@

```{r}
g_ir_yield_both <-
  results[, .(crop, yhat_data)] %>%
  dplyr::mutate(plot_data = purrr::map2(yhat_data, crop, \(yhat_data, crop) {
    yhat_data[, sat_cat_text := case_when(
      sat_cat == "[39.4,82]" ~ "1st quantile - [12, 25]",
      sat_cat == "(82,194]" ~ "2nd quantile - (25, 59.1]",
      sat_cat == "(194,708]" ~ "3rd quantile - (59.1, 215]",
      sat_cat == "dryland" ~ "Rainfed"
    )] %>%
      .[, sat_cat_text := factor(
        sat_cat_text,
        levels = c("Rainfed", "1st quantile - [12, 25]", "2nd quantile - (25, 59.1]", "3rd quantile - (59.1, 215]")
      )] %>%
      .[, crop_type := crop] %>%
      .[, crop_type := case_when(
        crop_type == "Corn" ~ "A. Corn",
        crop_type == "Soybean" ~ "(b) Sybean"
      )]
  })) %>%
  dplyr::mutate(g_yield = purrr::map(plot_data, \(plot_data) {
    ggplot(plot_data) +
      geom_line(aes(
        y = y_hat,
        x = balance,
        color = factor(sat_cat_text)
      )) +
      scale_x_continuous(
        name = "Water Deficit (mm)",
        breaks = (-2:11) * 100
      ) +
      scale_y_continuous(
        name = "Yield (tonne/ha)",
        breaks = 0:(ceiling(max(plot_data$y_hat)) + 0.5),
        limits = c(NA, (ceiling(max(plot_data$y_hat)) + 0.5))
      ) +
      scale_color_discrete(
        name = "Aquifer Thickness",
        guide = guide_legend(
          title.position = "top",
          nrow = 2
        )
      ) +
      scale_fill_discrete(guide = "none") +
      theme_fig +
      coord_cartesian(xlim = c(-200, 1150)) +
      theme(legend.position = "bottom")
  }))

@@

g_wds <-
  results[, .(crop, data)] %>%
  dplyr::mutate(g_fig = purrr::map(
    data,
    function(data) {
      ggplot(data) +
        geom_histogram(aes(x = balance), bins = 50, col = "darkgreen", fill = NA) +
        theme_fig +
        xlab("Water Deficit (mm)") +
        ylab("") +
        theme_void()
    }
  ))

@@

#++++++++++++++++++++++++++++++++++++
#+ With confidence interval (seprately)
#++++++++++++++++++++++++++++++++++++
g_yield_with_conf <-
  results[, .(crop, yhat_data)] %>%
  dplyr::mutate(plot_data = purrr::map2(yhat_data, crop, \(yhat_data, crop) {
    yhat_data[, sat_cat_text := case_when(
      sat_cat == "[39.4,82]" ~ "1st quantile - [12, 25]",
      sat_cat == "(82,194]" ~ "2nd quantile - (25, 59.1]",
      sat_cat == "(194,708]" ~ "3rd quantile - (59.1, 215]",
      sat_cat == "dryland" ~ "Rainfed"
    )] %>%
      .[, sat_cat_text := factor(
        sat_cat_text,
        levels = c("Rainfed", "1st quantile - [12, 25]", "2nd quantile - (25, 59.1]", "3rd quantile - (59.1, 215]")
      )] %>%
      .[, crop_type := crop] %>%
      .[, crop_type := case_when(
        crop_type == "Corn" ~ "A. Corn",
        crop_type == "Soybean" ~ "(b) Sybean"
      )]
  })) %>%
  mutate(g_fig = purrr::map(
    plot_data,
    \(plot_data) {
      ggplot(plot_data) +
        geom_ribbon(
          aes(
            ymin = y_hat - 1.96 * y_hat_se,
            ymax = y_hat + 1.96 * y_hat_se,
            x = balance
          ),
          alpha = 0.3
        ) +
        geom_line(aes(
          y = y_hat,
          x = balance
        )) +
        facet_wrap(~sat_cat_text, ncol = 2) +
        scale_x_continuous(
          name = "Water Deficit (mm)",
          breaks = (-1:5) * 200
        ) +
        scale_y_continuous(
          name = "Yield (tonne/ha)",
          breaks = 0:13
        ) +
        theme_fig +
        theme(
          legend.position = "bottom",
          strip.background = element_blank()
        )
    }
  )) %>%
  dplyr::select(crop, g_fig) %>%
  data.table()

ggsave("Shared/Results/g_yield_with_conf_corn.pdf", g_yield_with_conf[crop == "Corn", g_fig][[1]], width = 6, height = 3.5)
ggsave("Shared/Results/g_yield_with_conf_soy.pdf", g_yield_with_conf[crop == "Soybean", g_fig][[1]], width = 6, height = 3.5)
```

@@

```{r}
plot_data_ir_share <-
  results[, .(crop, share_pred_data)] %>%
  unnest(cols = share_pred_data) %>%
  data.table() %>%
  .[, crop_type := case_when(
    crop == "Corn" ~ "A. Corn",
    crop == "Soybean" ~ "B. Soybean"
  )]

g_share <-
  ggplot(plot_data_ir_share[sat <= 500, ]) +
  geom_line(aes(y = ir_share_hat, x = sat * 0.3048)) +
  geom_ribbon(
    aes(
      ymin = ir_share_hat - 1.96 * ir_share_hat_se,
      ymax = ir_share_hat + 1.96 * ir_share_hat_se,
      x = sat * 0.3048
    ),
    alpha = 0.4
  ) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 10)) +
  xlab("Aquifer Thickness (meter)") +
  ylab("Estimated Share of Irrigated Acres") +
  facet_wrap(crop_type ~ ., ncol = 1) +
  theme_fig +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold", family = "Times", size = )
  )

@@

```{r}
g_total_both <-
  rbindlist(results$avg_yield_data) %>%
  .[, crop_type := case_when(
    type == "Corn" ~ "A. Corn",
    type == "Soybean" ~ "B. Soybean"
  )] %>%
  .[, sat_m := measurements::conv_unit(sat, "ft", "m") %>% format(digits = 3)] %>%
  nest_by(crop_type) %>%
  data.table() %>%
  dplyr::mutate(g_fig = purrr::map(data, \(data) {
    ggplot(data) +
      geom_line(aes(y = avg_yield, x = balance, color = sat_m)) +
      theme_fig +
      ylim(min(data$avg_yield) - 0.5, max(data$avg_yield) + 0.5) +
      ylab("Yield (tonne/ha)") +
      scale_color_discrete(
        "Aquifer Thickness (meter)",
        guide = guide_legend(
          title.position = "top",
          nrow = 1
        )
      ) +
      scale_x_continuous(name = "Water Deficit (mm)", breaks = (-2:11) * 100, limits = c(-200, 1200)) +
      theme(legend.position = "bottom")
  }))

@@

g_avg_yield_dif <-
  boot_results_data[, .(crop, boot_results)] %>%
  unnest(cols = c(boot_results)) %>%
  data.table() %>%
  .[, .(
    dif_yield = mean(dif_yield),
    lower = quantile(dif_yield, prob = 0.05),
    upper = quantile(dif_yield, prob = 0.95)
  ),
  by = .(sat, balance, crop)
  ] %>%
  .[, sat_text := paste0(
    "Aquifer Thickness = ",
    measurements::conv_multiunit(sat, "ft", "m") %>% format(digits = 3),
    " meter"
  )] %>%
  .[sat != 40, ] %>%
  nest_by(crop) %>%
  data.table() %>%
  dplyr::mutate(g_fig = purrr::map(data, \(data){
    ggplot(data) +
      geom_ribbon(aes(x = balance, ymin = lower, ymax = upper), alpha = 0.3, fill = "blue") +
      geom_line(aes(x = balance, y = dif_yield), color = "red") +
      geom_hline(yintercept = 0) +
      facet_grid(. ~ sat_text, scales = "free_y") +
      xlab("Water Deficit (mm)") +
      ylab("Difference in Yield (tonne/ha)") +
      xlim(-200, 1200) +
      theme_fig +
      theme(
        strip.background = element_blank(),
        strip.text = element_text(size = 9, family = "Times"),
        panel.spacing.y = unit(1, "cm")
      )
  }))

@@

```{r}
g_ay_response <-
  boot_results_data[, .(crop, boot_results)] %>%
  unnest(cols = c(boot_results)) %>%
  data.table() %>%
  .[, .(
    avg_yield = mean(avg_yield),
    lower = quantile(avg_yield, prob = 0.05),
    upper = quantile(avg_yield, prob = 0.95)
  ),
  by = .(sat, balance, crop)
  ] %>%
  .[, sat_text := paste0(
    "Aquifer Thickness = ",
    measurements::conv_multiunit(sat, "ft", "m") %>% format(digits = 3),
    " meter"
  )] %>%
  nest_by(crop) %>%
  data.table() %>%
  dplyr::mutate(g_fig = purrr::map(data, \(data) {
    ggplot(data) +
      geom_ribbon(aes(x = balance, ymin = lower, ymax = upper), alpha = 0.3) +
      geom_line(aes(x = balance, y = avg_yield)) +
      facet_grid(. ~ sat_text, scales = "free_y") +
      ylim(min(data$avg_yield) - 1, max(data$avg_yield) + 0.5) +
      xlab("Water Deficit (mm)") +
      ylab("Yield (tonne/ha)") +
      theme_fig +
      theme(
        strip.background.x = element_blank(),
        panel.spacing = unit(0.1, "cm")
      )
  }))

>>>>

```{r}
results <- readRDS("Shared/Results/reg_results_data.rds")
all_results <- readRDS("Shared/Results/all_results.rds")

```

@@

g_corn <-
  ggplot() +
  geom_sf(data = counties_corn_all, fill = "gray") +
  geom_sf(data = counties_corn_ir, aes(fill = sat * 0.3048)) +
  scale_fill_viridis_c(
    name = "Aquifer Thickness (meter)",
    guide = guide_colorbar(
      title.position = "top"
    )
  ) +
  geom_sf(data = states_of_interest, fill = NA, color = "blue") +
  geom_sf(data = hpa_simplified, fill = NA, color = "red") +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(1, "cm"),
    plot.title = element_text(size = 9, family = "Times"),
    legend.title = element_text(family = "Times"),
    legend.text = element_text(family = "Times")
  ) +
  ggtitle("A. Corn")

g_soy <-
  ggplot() +
  geom_sf(data = counties_soy_all, fill = "gray") +
  geom_sf(data = counties_soy_ir, aes(fill = sat * 0.3048)) +
  scale_fill_viridis_c(
    name = "Aquifer Thickness (meter)",
    guide = guide_colorbar(
      title.position = "top"
    )
  ) +
  geom_sf(data = states_of_interest, fill = NA, color = "blue") +
  geom_sf(data = hpa_simplified, fill = NA, color = "red") +
  theme_void() +
  theme(
    legend.position = "bottom",
    legend.key.width = unit(1, "cm"),
    plot.title = element_text(size = 9, family = "Times"),
    legend.title = element_text(family = "Times"),
    legend.text = element_text(family = "Times")
  ) +
  ggtitle("B. Soybean")

@@

```{r}
g_ir_yield_both <-
  all_results[, .(crop, yield_response_sum)] %>%
  dplyr::mutate(plot_data = purrr::map2(yield_response_sum, crop, \(x, crop) {
    x[, sat_cat_text := case_when(
      sat_cat == "[39.4,82]" ~ "1st quantile: [12m, 25m]",
      sat_cat == "(82,194]" ~ "2nd quantile: (25m, 59.1m]",
      sat_cat == "(194,708]" ~ "3rd quantile: (59.1m, 215m]",
      sat_cat == "dryland" ~ "Rainfed"
    )] %>%
      .[, sat_cat_text := factor(
        sat_cat_text,
        levels = c("Rainfed", "1st quantile: [12m, 25m]", "2nd quantile: (25m, 59.1m]", "3rd quantile: (59.1m, 215m]")
      )] %>%
      .[, crop_type := crop] %>%
      .[, crop_type := case_when(
        crop_type == "corn" ~ "A. Corn",
        crop_type == "soy" ~ "(b) Sybean"
      )]
  })) %>%
  dplyr::mutate(g_yield = purrr::map(plot_data, \(plot_data) {
    ggplot(plot_data) +
      geom_line(aes(
        y = y_hat,
        x = balance,
        color = factor(sat_cat_text)
      )) +
      scale_x_continuous(
        name = "Water Deficit (mm)",
        breaks = (-2:11) * 100
      ) +
      scale_y_continuous(
        name = "Yield (tonne/ha)",
        breaks = 0:(ceiling(max(plot_data$y_hat)) + 0.5),
        limits = c(NA, (ceiling(max(plot_data$y_hat)) + 0.5))
      ) +
      scale_color_discrete(
        name = "Aquifer Thickness",
        guide = guide_legend(
          title.position = "top",
          nrow = 2
        )
      ) +
      scale_fill_discrete(guide = "none") +
      theme_fig +
      coord_cartesian(xlim = c(-200, 1150)) +
      theme(legend.position = "bottom")
  }))

@@

g_wds <-
  all_results[, .(crop, data)] %>%
  dplyr::mutate(g_fig = purrr::map(
    data,
    function(data) {
      ggplot(data) +
        geom_histogram(aes(x = balance), bins = 50, col = "darkgreen", fill = NA) +
        theme_fig +
        xlab("Water Deficit (mm)") +
        ylab("") +
        theme_void()
    }
  ))

@@

#++++++++++++++++++++++++++++++++++++
#+ With confidence interval (seprately)
#++++++++++++++++++++++++++++++++++++
g_yield_with_conf <-
  all_results[, .(crop, yield_response_sum)] %>%
  dplyr::mutate(plot_data = purrr::map2(yield_response_sum, crop, \(x, crop) {
    x[, sat_cat_text := case_when(
      sat_cat == "[39.4,82]" ~ "1st quantile: [12m, 25m]",
      sat_cat == "(82,194]" ~ "2nd quantile: (25m, 59.1m]",
      sat_cat == "(194,708]" ~ "3rd quantile: (59.1m, 215m]",
      sat_cat == "dryland" ~ "Rainfed"
    )] %>%
      .[, sat_cat_text := factor(
        sat_cat_text,
        levels = c("Rainfed", "1st quantile: [12m, 25m]", "2nd quantile: (25m, 59.1m]", "3rd quantile: (59.1m, 215m]")
      )] %>%
      .[, crop_type := crop] %>%
      .[, crop_type := case_when(
        crop_type == "corn" ~ "A. Corn",
        crop_type == "soy" ~ "(b) Sybean"
      )]
  })) %>%
  mutate(g_fig = purrr::map(
    plot_data,
    \(plot_data) {
      ggplot(plot_data) +
        geom_ribbon(
          aes(
            ymin = lower,
            ymax = upper,
            x = balance
          ),
          alpha = 0.3
        ) +
        geom_line(aes(
          y = y_hat,
          x = balance
        )) +
        facet_wrap(~sat_cat_text, ncol = 2) +
        scale_x_continuous(
          name = "Water Deficit (mm)",
          breaks = (-1:5) * 200
        ) +
        scale_y_continuous(
          name = "Yield (tonne/ha)",
          breaks = 0:13
        ) +
        theme_fig +
        theme(
          legend.position = "bottom",
          strip.background = element_blank()
        )
    }
  )) %>%
  dplyr::select(crop, g_fig) %>%
  data.table()

ggsave("Shared/Results/g_yield_with_conf_corn.pdf", g_yield_with_conf[crop == "corn", g_fig][[1]], width = 6, height = 3.5)
ggsave("Shared/Results/g_yield_with_conf_soy.pdf", g_yield_with_conf[crop == "soy", g_fig][[1]], width = 6, height = 3.5)
```

@@

```{r}
plot_data_ir_share <-
  all_results[, .(crop, share_sum)] %>%
  unnest(cols = share_sum) %>%
  data.table() %>%
  .[, crop_type := case_when(
    crop == "corn" ~ "A. Corn",
    crop == "soy" ~ "B. Soybean"
  )]

g_share <-
  ggplot(plot_data_ir_share[sat <= 500, ]) +
  geom_line(aes(y = ir_share_hat, x = sat * 0.3048)) +
  geom_ribbon(
    aes(
      ymin = lower,
      ymax = upper,
      x = sat * 0.3048
    ),
    alpha = 0.4
  ) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  scale_x_continuous(breaks = seq(10, 160, by = 10)) +
  xlab("Aquifer Thickness (meter)") +
  ylab("Estimated Share of Irrigated Acres") +
  facet_wrap(crop_type ~ ., ncol = 1) +
  theme_fig +
  theme(
    legend.position = "bottom",
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold", family = "Times", size = )
  )

@@

```{r}
g_total_both <-
  all_results[, .(crop, avg_yield_sum)] %>%
  unnest() %>%
  data.table() %>%
  .[, crop_type := case_when(
    crop == "corn" ~ "A. Corn",
    crop == "soy" ~ "B. Soybean"
  )] %>%
  .[, sat_m := measurements::conv_unit(sat, "ft", "m") %>% format(digits = 3)] %>%
  nest_by(crop_type) %>%
  data.table() %>%
  dplyr::mutate(g_fig = purrr::map(data, \(data) {
    ggplot(data) +
      geom_line(aes(y = avg_yield, x = balance, color = sat_m)) +
      theme_fig +
      ylim(min(data$avg_yield) - 0.5, max(data$avg_yield) + 0.5) +
      ylab("Yield (tonne/ha)") +
      scale_color_discrete(
        "Aquifer Thickness (meter)",
        guide = guide_legend(
          title.position = "top",
          nrow = 1
        )
      ) +
      scale_x_continuous(name = "Water Deficit (mm)", breaks = (-2:11) * 100, limits = c(-200, 1200)) +
      theme(legend.position = "bottom")
  }))

@@

g_avg_yield_dif <-
  boot_results_data[, .(crop, boot_results)] %>%
  unnest(cols = c(boot_results)) %>%
  data.table() %>%
  .[, .(
    dif_yield = mean(dif_yield),
    lower = quantile(dif_yield, prob = 0.05),
    upper = quantile(dif_yield, prob = 0.95)
  ),
  by = .(sat, balance, crop)
  ] %>%
  .[, sat_text := paste0(
    "Aquifer Thickness = ",
    measurements::conv_multiunit(sat, "ft", "m") %>% format(digits = 3),
    "m"
  )] %>%
  .[sat != 40, ] %>%
  nest_by(crop) %>%
  data.table() %>%
  dplyr::mutate(g_fig = purrr::map(data, \(data){
    ggplot(data) +
      geom_ribbon(aes(x = balance, ymin = lower, ymax = upper), alpha = 0.3, fill = "blue") +
      geom_line(aes(x = balance, y = dif_yield), color = "red") +
      geom_hline(yintercept = 0) +
      facet_grid(. ~ sat_text, scales = "free_y") +
      xlab("Water Deficit (mm)") +
      ylab("Difference in Yield (tonne/ha)") +
      xlim(-200, 1200) +
      theme_fig +
      theme(
        strip.background = element_blank(),
        strip.text = element_text(size = 9, family = "Times"),
        panel.spacing.y = unit(1, "cm")
      )
  }))

@@

```{r}
g_ay_response <-
  boot_results_data[, .(crop, boot_results)] %>%
  unnest(cols = c(boot_results)) %>%
  data.table() %>%
  .[, .(
    avg_yield = mean(avg_yield),
    lower = quantile(avg_yield, prob = 0.05),
    upper = quantile(avg_yield, prob = 0.95)
  ),
  by = .(sat, balance, crop)
  ] %>%
  .[, sat_text := paste0(
    "Aquifer Thickness = ",
    measurements::conv_multiunit(sat, "ft", "m") %>% format(digits = 3),
    "m"
  )] %>%
  nest_by(crop) %>%
  data.table() %>%
  dplyr::mutate(g_fig = purrr::map(data, \(data) {
    ggplot(data) +
      geom_ribbon(aes(x = balance, ymin = lower, ymax = upper), alpha = 0.3) +
      geom_line(aes(x = balance, y = avg_yield)) +
      facet_grid(. ~ sat_text, scales = "free_y") +
      ylim(min(data$avg_yield) - 1, max(data$avg_yield) + 0.5) +
      xlab("Water Deficit (mm)") +
      ylab("Yield (tonne/ha)") +
      theme_fig +
      theme(
        strip.background.x = element_blank(),
        panel.spacing = unit(0.1, "cm")
      )
  }))
